---
title: "Data Availability Check"
output: html_document
---

```{r pacakges, cache = FALSE, echo = FALSE}
# === packages ===#
library(data.table)
library(flextable)
library(officer)
```

```{r, cache = F, echo = F}
library(knitr)
knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  warning = FALSE,
  cache.lazy = FALSE,
  fig.retina = 6,
  fig.height = 9,
  fig.width = 9,
  message = FALSE
)
```

# Field Parameter Data Anomalies 

```{r }
field_data <- jsonlite::fromJSON(
  here("Data", "CommonData", "fp_new_DSB.json"),
  flatten = TRUE
) %>%
data.table() %>%
.[, field_year := paste(farm, field, year, sep = "_")]

``` 

## Duplicates

```{r }
duplicate_entries <- field_data[, .(num_entries = .N), by = field_year] %>% 
  .[num_entries > 1, ]
```

Here is the list of `farm_field_year` that has duplicate entries:

```{r }
flextable(duplicate_entries) 
```

## Folders without an entry in the field parameter data


```{r eval = F}
all_dirs <- list.files(here("Data", "Growers"))  

is_dir_valid <- all_dirs %in% field_year_ls   
```

Here is the list of data directories that do not have any entry in `field_parameter.json`:

```{r }
all_dirs[!is_dir_valid]
```

This happened because `initiate_fp_entry()` (available in `tools_for_trial_design_coordinators.R`) was not used to create the folders for these experiments. 

## Raw data inconsistency

```{r }

check_file_consistency <- function(ffy) {
  #--- get input data ---#
  input_data <- field_data[field_year == ffy, ] %>% 
    dplyr::select(starts_with("input")) %>% 
    map(1) %>% 
    rbindlist(fill = TRUE) %>% 
    rowwise() %>% 
    mutate(
      status = function(){

        if (data == "received") {

        } else if (data == "not received") {

          return("ask for the data")

        } else {


        }

      }
    )
  
}


```


# Field parameter (except input data) anomalies

```{r error = TRUE}
#--- field data parameter dictionary ---#
# does not include input parameter dictionary

field_data_dict <- jsonlite::fromJSON(
  file.path(
    here("Data", "CommonData"),
    "field_parameter_dictionary.json"
  ),
  flatten = TRUE
) %>%
data.table()

check_validity <- function (ffy) {

  w_field_data <- field_data[field_year == ffy, ]
  # w_field_data <- field_data[1, ]

  data_validity_tab <- data.table(
    crop = ifelse(
      w_field_data$crop %in% field_data_dict$crop[[1]],
      "valid",
      "invalid"
    )
  ) %>% 
  .[, raw_yield := ifelse(
    w_field_data$raw_yield %in% field_data_dict$raw_yield[[1]],
    "valid",
    "invalid (NA not allowed)"
  )] %>% 
  #--- crop price ---#
  .[, crop_price := ifelse(
    is.numeric(w_field_data$crop_price),
    "valid",
    "entry must be numeric"
  )] %>%
  .[, crop_price := ifelse(
    is.na(w_field_data$crop_price),
    "missing",
    crop_price
  )] %>% 
  #--- crop unit ---#
  .[, crop_unit := ifelse(
    w_field_data$crop_unit %in% field_data_dict$crop_unit[[1]],
    "valid",
    "unsupported unit used (NA not allowed)"
  )] %>%
  #--- raw yield ---#
  .[, raw_yield := ifelse(
    w_field_data$raw_yield %in% field_data_dict$raw_yield[[1]],
    "valid",
    "invalid (NA not allowed)"
  )] %>%  
  #--- harvester width ---#
  .[, h_width := ifelse(
    is.numeric(w_field_data$h_width),
    "valid",
    "entry must be numeric (NA not allowed)"
  )] %>% 
  #--- ec ---#
  .[, ec := ifelse(
    w_field_data$ec %in% field_data_dict$ec[[1]],
    "valid",
    "invalid (NA not allowed)"
  )] %>% 
  #--- soil sampling ---#
  .[, soil_sampling := ifelse(
    w_field_data$soil_sampling %in% field_data_dict$soil_sampling[[1]],
    "valid",
    "invalid (NA not allowed)"
  )] 

}

lapply(field_year_ls, check_validity) %>% 
  rbindlist() %>% 
  flextable() %>%
  color(
    color = "blue"
  ) %>% 
  color(
    i = ~ crop != "valid",
    j = ~ crop,
    color = "red"
  )  %>% 
  color(
    i = ~ raw_yield != "valid",
    j = ~ raw_yield,
    color = "red"
  ) %>% 
  color(
    i = ~ crop_price != "valid",
    j = ~ crop_price,
    color = "red"
  ) %>% 
  color(
    i = ~ crop_unit != "valid",
    j = ~ crop_unit,
    color = "red"
  ) %>% 
  color(
    i = ~ h_width != "valid",
    j = ~ h_width,
    color = "red"
  ) %>% 
  color(
    i = ~ ec != "valid",
    j = ~ ec,
    color = "red"
  ) %>% 
  color(
    i = ~ soil_sampling != "valid",
    j = ~ soil_sampling,
    color = "red"
  ) %>% 
  flextable::align(
    align = "center",
    part = "all"
  )%>% 
  fontsize(
    size = 18,
    part = "all"
  ) %>%
  autofit()

```

## Input parameter anomalies

```{r error = TRUE}
#--- input parameter dictionary ---#
input_data_dict_v <- jsonlite::fromJSON(
  file.path(
    here("Data", "CommonData"),
    "field_parameter_dictionary_inputs.json"
  ),
  flatten = TRUE
) 

lapply(field_year_ls, check_input_validity) %>% 
  rbindlist()

check_input_validity <- function(ffy){

  input_data <- field_data[field_year == ffy, ] %>% 
  # input_data <- field_data[18, ] %>% 
    dplyr::select(starts_with("input."))

  #--- ignore empty input data ---#
  input_ls <- input_data %>% 
    lapply(., function(x) is.data.frame(x[[1]])) %>% 
    unlist() %>% 
    names(input_data)[.]

  input_validity <- list() 

  # w_input <- "input.1"
  for (w_input in input_ls){

    w_input_data <- input_data[, w_input, with = FALSE][[1]][[1]]

    if (w_input_data$form == "seed") {
      temp_data <- data.table(
        price = ifelse(
          is.numeric(w_input_data$price),
          "valid",
          "invalid (NA not allowed)"
        ),
        data = ifelse(
          w_input_data$data %in% input_data_dict_v$data[[1]],
          "valid",
          "invalid"
        ),
        sq_rate = ifelse(
          is.numeric(w_input_data$sq_rate) | is.na(w_input_data$sq_rate),
          "valid",
          "invalid"
        ),
        Rx_exists = ifelse(
          w_input_data$Rx_exists %in% input_data_dict_v$Rx_exists[[1]],
          "valid",
          "invalid"
        ), 
        machine_width = ifelse(
          is.numeric(w_input_data$machine_width) | is.na(w_input_data$machine_width),
          "valid",
          "invalid"
        ), 
        machine_sections = ifelse(
          is.numeric(w_input_data$machine_sections) | is.na(w_input_data$machine_sections),
          "valid",
          "invalid"
        ),
        use_target_rate_instead = ifelse(
          is.logical(w_input_data$use_target_rate_instead) | is.na(w_input_data$use_target_rate_instead),
          "valid",
          "invalid"
        ),
        input = w_input
      )  

      if (w_input == "seed") {
        temp_data[, unit := w_input_data$unit %in% (input_data_dict_v$unit[[1]] %>% .[str_detect(., "seed")])]
      } else {
        temp_data[, unit := w_input_data$unit %in% (input_data_dict_v$unit[[1]] %>% .[!str_detect(., "seed")])]
      }
    } else {
      # if the input type is "N_base"
      temp_data <- data.table(
        price = is.numeric(w_input_data$price),
        unit = w_input_data$unit %in% (input_data_dict_v$unit[[1]] %>% .[str_detect(., "seed")]),
        rate = is.numeric(w_input_data$price),
        input = w_input
      )
    }

  input_validity[[w_input]] <- temp_data

  }

  return(rbindlist(input_validity, fill = TRUE))

}



```

# Raw Data Availability 

```{r error = TRUE}

field_data <- jsonlite::fromJSON(
  file.path(
    here("Data", "CommonData"),
    "fp_latest.json"
  ),
  flatten = TRUE
) %>%
data.table() %>%
.[, field_year := paste(farm, field, year, sep = "_")] %>% 
.[, farm_field := paste(farm, field, sep = "_")]

check_availability <- function(ffy) {

  print(ffy)

  raw_data_path <- here("Data", "Growers", ffy, "Raw")
  analysis_data_path <- here("Data", "Growers", ffy, "Analysis-Ready")

  #/*----------------------------------*/
  #' ## Field data
  #/*----------------------------------*/
  w_field_data <- field_data[field_year == ffy, ]  

  #--- get input data ---#
  input_data <- select(w_field_data, starts_with("input.")) %>% 
    lapply(., function(x) x[[1]]) %>% 
    rbindlist(fill = TRUE)
  
  #--- seed trial? ---#
  is_trial_s <- "seed" %in% input_data[strategy == "trial", form]

  if (is_trial_s) {
    use_td_s <- input_data[form == "seed", use_target_rate_instead]
  } else {
    use_td_s <- FALSE
  }

  #--- nitrogen trial? ---#
  n_var_ls <- c("NH3", "urea", "uan32", "uan28")
  process_n_idv <- n_var_ls %in% input_data[strategy == "trial", form]
  is_trial_n <- any(process_n_idv)

  if (is_trial_n) {
    n_var <- n_var_ls[process_n_idv]
    use_td_n <- input_data[form == n_var, use_target_rate_instead]
  } else {
    use_td_n <- FALSE  
  }

  #--- K trial? ---#
  is_trial_k <- "K" %in% input_data[strategy == "trial", form]

  if (is_trial_k) {
    use_td_k <- input_data[form == "K", use_target_rate_instead]
  } else {
    use_td_k <- FALSE
  }

  #/*----------------------------------*/
  #' ## Create a table
  #/*----------------------------------*/
  return_table <- data.table(
    raw_yield = ifelse(
      file.exists(file.path(raw_data_path, "raw-yield.shp")),
      "available", 
      "not available"
    ),
    as_applied_s = ifelse(
      file.exists(file.path(raw_data_path, "as-applied-s.shp")),
      "available", 
      "not available"
    ),
    as_applied_n = ifelse(
      file.exists(file.path(raw_data_path, "as-applied-n.shp")),
      "available", 
      "not available"
    ),
    as_applied_k = ifelse(
      file.exists(file.path(raw_data_path, "as-applied-k.shp")),
      "available", 
      "not available"
    ),
    ec = ifelse(
      file.exists(file.path(raw_data_path, "ec.shp")),
      "available", 
      "not available"
    ),
    soil_sampling = ifelse(
      file.exists(file.path(raw_data_path, "soil-sampling.shp")),
      "available", 
      "not available"
    ),
    boundary = ifelse(
      file.exists(file.path(raw_data_path, "boundary.shp")),
      "available", 
      "not available"
    ),
    ab_line = ifelse(
      file.exists(file.path(raw_data_path, "ab-line.shp")),
      "available", 
      "not available"
    )
  ) %>%
  .[, field_year := ffy] %>%
  .[, field := unique(w_field_data$farm_field)] %>%
  .[, year := unique(w_field_data$year)] %>%
  .[, trial_type := case_when(
      is_trial_s & is_trial_n ~ "SN",
      is_trial_s & !is_trial_n ~ "S",
      is_trial_n & !is_trial_s ~ "N",
      is_trial_k ~ "K"
  )] %>% 
  .[, e_processing := "Not ready"] %>%
  .[trial_type == "SN" & as_applied_s == "available" & as_applied_n == "available", e_processing := "Ready to process"] %>%
  .[trial_type == "S" & as_applied_s == "available", e_processing := "Ready to process"] %>%
  .[trial_type == "N" & as_applied_n == "available", e_processing := "Ready to process"] %>%
  .[trial_type == "K" & as_applied_k == "available", e_processing := "Ready to process"] %>%
  .[, as_applied_s := ifelse(is_trial_s, as_applied_s, "irrelevant")] %>% 
  .[, as_applied_n := ifelse(is_trial_n, as_applied_n, "irrelevant")] %>% 
  .[, as_applied_k := ifelse(is_trial_k, as_applied_k, "irrelevant")] %>% 
  .[, as_applied_s := ifelse(!use_td_s, as_applied_s, "use trial design")] %>% 
  .[, as_applied_n := ifelse(!use_td_n, as_applied_n, "use trial design")] %>% 
  .[, as_applied_k := ifelse(!use_td_k, as_applied_k, "use trial design")] %>% 
  .[, trial_data_design := "Not ready"] %>% 
  .[ab_line == TRUE & boundary == TRUE, trial_data_design := "Ready"] %>% 
  relocate(field_year, field, year, trial_type)

  return(return_table)
}

lapply(field_year_ls, check_availability) %>%
  rbindlist() %>% 
  .[order(field, year),] %>% 
  flextable() %>%
  color(
    j = c(3:5, 10),
    color = "blue"
  ) %>% 
  color(
    i = ~ as_applied_s == "not available",
    j = ~ as_applied_s,
    color = "red"
  ) %>%
  color(
    i = ~ as_applied_s == "irrelevant",
    j = ~ as_applied_s,
    color = "gray"
  ) %>%
  color(
    i = ~ as_applied_n == "not available",
    j = ~ as_applied_n,
    color = "red"
  ) %>%
  color(
    i = ~ as_applied_n == "irrelevant",
    j = ~ as_applied_n,
    color = "gray"
  ) %>%
  color(
    i = ~ as_applied_k == "not available",
    j = ~ as_applied_k,
    color = "red"
  ) %>%
  color(
    i = ~ as_applied_k == "irrelevant",
    j = ~ as_applied_k,
    color = "gray"
  ) %>%
  color(
    i = ~ raw_yield == "not available",
    j = ~ raw_yield,
    color = "red"
  )%>%
  color(
    i = ~ e_processing == "Not ready",
    j = ~ e_processing,
    color = "red"
  ) %>%
  flextable::align(
    align = "center",
    part = "all"
  )%>% 
  fontsize(
    size = 18,
    part = "all"
  ) %>%
  autofit  

```

# Non-experiment Intermediate Data Availability Status

```{r }
check_availability_ne <- function(ffy) {
  return_table <- data.table(
    Topography = file.exists(
      file.path(
        here("Data", "Growers", ffy, "Intermediate"),
        "topography.rds"
      )
    ),
    SSURGO = file.exists(
      file.path(
        here("Data", "Growers", ffy, "Intermediate"),
        "ssurgo.rds"
      )
    ),
    Weather = file.exists(
      file.path(
        here("Data", "Growers", ffy, "Intermediate"),
        "weather_daymet.rds"
      )
    ),
    EC = file.exists(
      file.path(
        here("Data", "Growers", ffy, "Intermediate"),
        "ec.rds"
      )
    )
  ) %>%
    .[, field_year := ffy]

  return(return_table)
}

lapply(field_year_ls, check_availability_ne) %>%
  rbindlist() %>%
  relocate(field_year) %>%
  flextable() %>%
  flextable::align(
    align = "center",
    part = "all"
  ) %>%
  fontsize(
    size = 18,
    part = "all"
  ) %>%
  autofit()
```

# Data availability for Analysis and Reporting

```{r }
check_availability_ar <- function(ffy) {
  return_table <- data.table(
    analysis_data.rds = file.exists(
      file.path(
        here("Data", "Growers", ffy, "Analysis-Ready"),
        "analysis_data.rds"
      )
    ),
    analysis_results.rds = file.exists(
      file.path(
        here("Reports", "Growers", ffy),
        "analysis_results.rds"
      )
    ),
    `grower-report.html` = file.exists(
      file.path(
        here("Reports", "Growers", ffy),
        "grower-report.html"
      )
    )
  ) %>%
    .[, field_year := ffy] %>%
    .[, `Run Analysis` := "Not ready"] %>%
    .[analysis_data.rds == TRUE, `Run Analysis` := "Ready"] %>%
    .[, `Make a Report` := "Not ready"] %>%
    .[analysis_results.rds == TRUE, `Make a Report` := "Ready"] %>% 
    .[, `Report Created` := "No"] %>%
    .[`grower-report.html` == TRUE, `Report Created` := "Yes"]

  return(return_table)
}

lapply(field_year_ls, check_availability_ar) %>%
  rbindlist() %>%
  relocate(field_year) %>%
  flextable() %>%
  flextable::align(
    align = "center",
    part = "all"
  ) %>%
  fontsize(
    size = 18,
    part = "all"
  ) %>%
  autofit()
```

