# What needs to happen

+ starting point has to be in the middle of the first plot
+ change plot length by row 
+ various designs of assigning seed and n (ensure orthogonality)
+ allow the design to be dependent on spatial variables


## Setting parameters

+ we assign seed rate by section of planter

+ least common multiple of the section width and harvester width is harvester width, there is no problem

+ could change the plot width 


# Prep

```{r }
library(sp)
library(sf)
library(here)
library(agricolae)
library(lwgeom)
library(measurements)
library(stringr)
library(tmap)
library(raster)
library(tidyverse)
library(data.table)
```

```{r }
#--- local ---#
source("Codes/TrialDesignGeneration/functions_for_trial_design.R")

#--- github ---#
source("https://raw.githubusercontent.com/brittanikedge/DIFM/main/Functions.R")

```

```{r map-layout}
tm_layout_to_add <- tm_layout(
  legend.outside = "TRUE",
  frame = FALSE,
  legend.title.size = 2,
  legend.text.size = 1.5
)
```

## Preparation

```{r }
ffy <- "Wendte_LaueLib80_2020"
ffy <- "Boeckner_134n_2017"

#--- field boundary ---#
field <- ffy %>% 
  file.path(here("Data", "Growers"), ., "Raw/boundary.shp") %>% 
  st_read() %>%
  st_make_valid() %>%
  st_transform_utm()

#--- ab-line ---#
ab_line <- ffy %>% 
  file.path(here("Data", "Growers"), ., "Raw/ab-line.shp") %>% 
  st_read() %>%
  st_make_valid() %>%
  st_transform_utm()

#--- field parameters ---#
field_data <- jsonlite::fromJSON(
  file.path(
    here("Data", "CommonData"),
    "fp_new_DSB.json"
  ),
  flatten = TRUE
) %>%
data.table() %>%
.[, field_year := paste(farm, field, year, sep = "_")] %>% 
.[field_year == ffy, ]

```   

```{r }
tm_shape(field) +
  tm_borders() +
  tm_shape(ab_line) +
  tm_lines(col = "red")
```

## Set parameters

```{r }
#--- temporary ---#
planter_width <- 60 %>%
  conv_unit(., "ft", "m")
planter_section_num <- 2
harvester_width <- 30 %>%
  conv_unit("ft", "m")
# applicator_width <- w_field_data[, a_width] %>%
#   conv_unit("ft", "m")
# applicator_section_num <- w_field_data[, a_section_no] %>%
#   conv_unit("ft", "m")

applicator_width <- 0

#--- headland length ---#
headland_length <- max(planter_width, harvester_width, applicator_width) * 2

```

# Create Trial Design

## Set parameters

```{r }
cell_height <- conv_unit(10, "ft", "m")

#--- this should be defined above  ---#
plot_width <- conv_unit(30, "ft", "m")
```

## Make experiment grids

```{r }
whole_field <- make_trial_grids(
  field = field, 
  ab_line = ab_line, 
  plot_width = plot_width, 
  cell_height = cell_height,
  headland_length = headland_length
)

experiment_plots <- whole_field$experiment

headland <- whole_field$headland

```

```{r }
tm_shape(field) +
  tm_borders(col = "black") + 
tm_shape(headland) +
  tm_fill(col = "red", alpha = 0.3) +
tm_shape(experiment_plots) +
  tm_fill(
    col = "strip_id", 
    palette = "Spectral", 
    style = "order"
  )  +
tm_layout_to_add

```

## Assigning rates

```{r }
rate_ls <- seq(90, 240, by = 30)

experiment_design <- assign_rates(
  data_sf = experiment_plots, 
  rates_ls = rate_ls
)  %>% 
select(rate)

grower_chosen_rate <- 180

headland <- mutate(
  headland, 
  rate = grower_chosen_rate
)

trial_design <- rbind(
  experiment_design,
  headland
)

```

```{r }
tm_td <- tm_shape(trial_design) +
  tm_fill(
    col = "rate", 
    palette = "YlGn", 
    style = "cat"
  ) + 
tm_shape(field) +
  tm_borders() +
tm_layout_to_add

tmap_save(tm_td, file = paste0(here("Data", "Disposable/TD_"), ffy, ".pdf"))

```

# Orthogonality check

```{r }
topography <- file.path(here("Data", "Growers", ffy), "Intermediate/topography.rds") %>% 
  readRDS()

ssurgo <- file.path(here("Data", "Growers", ffy), "Intermediate/ssurgo.rds") %>% 
  readRDS()

trial_design
  
```

