# Preparation

## Read boundary and ab-line

```{r }
# ffy <- "Wendte_LaueLib80_2020"
# ffy <- "Boeckner_134n_2017"
# ffy <- "Bohnhoff_Adams_2018"
# ffy <- "Holzwart_Holzwart_2021"

#--- field boundary ---#
field <- here("Data", "Growers", ffy, "TrialDesign/boundary.shp") %>% 
  st_read() %>% 
  st_set_4326() %>% 
  st_make_valid() %>%
  st_transform_utm()

#--- ab-line ---#
if (use_ab) {
  ab_line <- here("Data", "Growers", ffy, "TrialDesign/ab-line.shp") %>% 
    #--- read the data ---#
    st_read() %>% 
    st_set_4326() %>% 
    st_make_valid() %>%
    st_transform_utm() 
} else {
  past_aa_input <- _past-aa-input-file-name-here_
  # past_aa_input <- past_aa_input_file %>% 
    #--- read the data ---#
    st_read() %>% 
    st_set_4326() %>% 
    st_make_valid() %>%
    st_transform_utm() 

  ab_line <- get_ab_line(past_aa_input) 
}

```

```{r }
tm_shape(field) +
  tm_borders() +
  tm_shape(ab_line) +
  tm_lines(col = "red")
```

## Field Parameters

```{r results = "hide"}
#--- read and define field parameters ---#
source(
  here("Codes/Functions/unpack_field_parameters.R"),
  local = TRUE
)

```   

## Option parameters

```{r }
#=== user-specified list of experimental rates ===#
rates_ls <- _rates-here_

#=== headland length ===#
headland_length <- conv_unit(
  _head-dist-here_,
  "ft", "m"
)

#=== plot-width ===#
plot_width <- conv_unit(
  _plot-width-here_,
  "ft", "m"
)

#=== status-quo rate ===#
gc_rate <- _gc-rate-here_

```

# Create Trial Design

## Set parameters

```{r }
#/*----------------------------------*/
#' ## Machine width
#/*----------------------------------*/
#--- planter width ---#
if (process_s) {
  planter_width <- input_data[form == "seed", machine_width] %>%
    conv_unit(., "ft", "m")
} else {
  planter_width <- 1
}

#--- applicator_width ---#
if (process_n) {
  applicator_width <- input_data[form == n_var, machine_width] %>%
    conv_unit(., "ft", "m")
} else {
  applicator_width <- 1
}

#--- harvester width ---#
harvester_width <- w_field_data[, h_width] %>%
  as.numeric() %>% 
  conv_unit(., "ft", "m")

#/*----------------------------------*/
#' ## Headland length
#/*----------------------------------*/
#--- headland length ---#
if (is.na(head_dist)) {
  headland_length <- max(planter_width, harvester_width, applicator_width) * 4
}

#--- get the least common multiple (needs to be changed) ---#

if (is.na(plot_width) & is.numeric(plot_width)) {
  plot_width <- Lcm(planter_width, harvester_width) %>%
    Lcm(., applicator_width)

  #--- this is temporary ---#
  plot_width <- max(planter_width, harvester_width)
}

#--- cell height ---#
cell_height <- conv_unit(10, "ft", "m")

```

## Make experiment grids

```{r }
#/*----------------------------------*/
#' ## Create experimental plots
#/*----------------------------------*/
experiment_plots <- make_trial_grids(
  field = field, 
  #--- by default uses the first one ---#
  ab_line = ab_line[1, ], 
  plot_width = plot_width, 
  cell_height = cell_height,
  headland_length = headland_length
)

#/*----------------------------------*/
#' ## Create headland
#/*----------------------------------*/
experiment_plots_dissolved <- experiment_plots %>% 
  st_snap_to_grid(size = 0.0001) %>%
  st_make_valid() %>% 
  summarize(plot_id = min(plot_id))

headland <- st_difference(field, experiment_plots_dissolved) %>%
  dplyr::select(geometry) %>% 
  #--- assign grower-chosen rate to the headland ---#
  mutate(rate = gc_rate)

```


```{r }
tm_shape(field) +
  tm_borders(col = "black") + 
tm_shape(headland) +
  tm_fill(
    col = "red", 
    alpha = 0.3, 
    title = "Headland"
  ) +
tm_shape(experiment_plots) +
  tm_fill(
    col = "strip_id", 
    palette = "Spectral", 
    style = "order"
  )  +
tm_layout_to_add

```

## Assigning rates


```{r }

if (!is.na(rates_ls)) {
#/*~~~~~~~~~~~~~~~~~~~~~~*/
#' ### If rates are provided by the user
#/*~~~~~~~~~~~~~~~~~~~~~~*/
  experiment_design <- assign_rates(
    data_sf = experiment_plots, 
    rates_ls = rates_ls,
    # pattern = "block_randomized"
    pattern = "fixed-latin-square"
    # pattern = "sequential"
  )  %>% 
  #--- keep cell_id here for orthogonality check later ---#
  dplyr::select(rate)

  trial_design <- rbind(
    experiment_design,
    headland
  )

} else {

#/*~~~~~~~~~~~~~~~~~~~~~~*/
#' ### If rate are NOT provided by the use
#/*~~~~~~~~~~~~~~~~~~~~~~*/
  trial_designs <- tibble(
    rates = list(
      c(0.5, 0.65, 0.8, 1, 1.15),
      c(0.5, 0.65, 0.8, 1, 1.15, 1.3),
      c(0.6, 0.75, 0.9, 1, 1.2),
      c(0.6, 0.75, 0.9, 1, 1.15, 1.3),
      seq(0.7, 1.2, by = 0.1),
      seq(0.7, 1.3, by = 0.15)   
    )
  ) %>% 
  rowwise() %>% 
  mutate(
    rates = list(
      rates * gc_rate
    )
  ) %>% 
  mutate(
    trial_design = list(
       assign_rates(
        data_sf = experiment_plots, 
        rates_ls = rates
      )  %>% 
      dplyr::select(rate) %>% 
      rbind(., headland)
    ) 
  ) %>% 
  mutate(
    td_map = list(
      tm_shape(trial_design) +
        tm_fill(
          col = "rate", 
          palette = "YlGn", 
          style = "cat"
        ) + 
      tm_shape(headland) +
        tm_borders(
          lwd = 4
        ) +
      tm_shape(ab_line) +
        tm_lines(
          col = "red",
          lwd = 4
        ) +
      tm_layout_to_add
    )
  )

  #--- show the designs ---#
  pluck(trial_designs, "td_map")

}

``` 

# Save the trial design

```{r eval = !is.na(rates_ls), echo = !is.na(rates_ls)}

trial_design_ll <- st_transform(trial_design, 4326)

time_user <- paste0(
  Sys.time(), 
  "-",
  Sys.getenv("USER")
) %>% 
gsub(" ", "-", .) %>% 
gsub("_", "-", .)  

dsn_name <- here("Data", "Growers", ffy, "TrialDesign")

st_write(
  trial_design_ll, 
  dsn = dsn_name,
  layer = paste0("trial-design-", time_user),
  driver = "ESRI Shapefile"
)

writeLines(
  paste0(
    "The trial design was named, trial-design-",
    time_user,
    ".shp"
  )
)
```

# Orthogonality check

Checking if the assigned rates are orthogonal to the soil and field characteristics. 

```{r results = "hide", eval = F}

topo <- file.path(here("Data", "Growers", ffy), "Intermediate/topography.rds") %>% 
  readRDS()

ssurgo <- file.path(here("Data", "Growers", ffy), "Intermediate/ssurgo.rds") %>% 
  readRDS()

topo_values <- topo %>%
  stars_to_stack() %>%
  exact_extract(., st_transform(experiment_design, st_crs(.))) %>%
  rbindlist(idcol = "rowid") %>%
  .[,
    lapply(.SD, weighted.mean, w = coverage_fraction),
    by = rowid,
    .SDcols = paste0("layer.", 1:length(topo))
  ] %>%
  .[, rowid := NULL] %>%
  setnames(names(.), names(topo))

experiment_design <- cbind(experiment_design, topo_values)

ssurgo_values <- dplyr::select(experiment_design, cell_id) %>%
  st_intersection(., ssurgo) %>%
  mutate(area = as.numeric(st_area(.))) %>%
  data.table() %>%
  .[, area_pct := area / sum(area), by = cell_id] %>%
  .[,
    lapply(.SD, weighted.mean, w = area_pct),
    by = cell_id,
    .SDcols = c("clay", "sand", "silt", "water_storage")
  ]

experiment_design <- left_join(experiment_design, ssurgo_values, by = "cell_id")
  
```

```{r eval = F}
#--- plot level ---#
experiment_design %>% 
  dplyr::select(where(is.numeric)) %>% 
  st_drop_geometry() %>% 
  data.table() %>% 
  .[, lapply(.SD, mean), by = .(plot_id, strip_id)] %>% 
  .[,`:=`(
    plot_id = NULL,
    strip_id = NULL
  )] %>% 
  cor() %>% 
  .[, "rate"] 

#--- cell-level ---#
experiment_design %>% 
  dplyr::select(where(is.numeric)) %>% 
  st_drop_geometry() %>% 
  data.table() %>% 
  .[, cell_id := NULL] %>% 
  cor() %>% 
  .[, "rate"] 

```


# Things to do 

+ allow the design to be dependent on spatial variables

## Setting parameters

+ optimal plot width
+ change the plot width in the middle 
