# What needs to happen

+ starting point has to be in the middle of the first plot
+ change plot length by row 
+ various designs of assigning seed and n (ensure orthogonality)
+ allow the design to be dependent on spatial variables


## Setting parameters

+ we assign seed rate by section of planter

+ least common multiple of the section width and harvester width is harvester width, there is no problem

+ could change the plot width 

# Prep 

```{r }
library(sp)
library(sf)
library(agricolae)
library(lwgeom)
library(measurements)
library(tmap)
library(raster)
library(data.table)
```

```{r }
#--- local ---#
source("Codes/TrialDesignGeneration/functions_for_trial_design.R")

#--- github ---#
source("https://raw.githubusercontent.com/brittanikedge/DIFM/main/Functions.R")
 ```

```{r map-layout}
tm_layout_to_add <- tm_layout(
  legend.outside = "TRUE",
  frame = FALSE,
  legend.title.size = 2,
  legend.text.size = 1.5
)
```

## Preparation

```{r }
design <- here("Data", "Disposable", "NK1_Polygons_pass_and_unique_pass.shp") %>%
  file.path() %>% 
  st_read()
```   

```{r }
tm_shape(design) +
  tm_polygons(col = "red", alpha = 0.4)
```

## Set parameters

```{r }
w_field_data <- field_data[field_year == ffy, ]

#--- widths of machines in meter ---#
planter_width <- w_field_data[, p_width] %>%
  conv_unit(., "ft", "m")
planter_section_num <- w_field_data[, p_section_no]
p_section_width <- planter_width / planter_section_num
harvester_width <- w_field_data[, h_width] %>%
  conv_unit("ft", "m")

#--- temporary ---#
planter_width <- 60 %>%
  conv_unit(., "ft", "m")
planter_section_num <- 2
harvester_width <- 30 %>%
  conv_unit("ft", "m")
# applicator_width <- w_field_data[, a_width] %>%
#   conv_unit("ft", "m")
# applicator_section_num <- w_field_data[, a_section_no] %>%
#   conv_unit("ft", "m")

applicator_width <- 0

#--- headland length ---#
headland_buffer <- max(planter_width, harvester_width, applicator_width) * 2
```

# Defining the optimal plot width

Note: optimal means least percentage of overlap

```{r best-design, eval = F}
field_width <- 1200
harvester_width <- 60
planter_section_width <- 24

max_multiplication <- ceiling((harvester_width %/% planter_section_width))

multiple_ls <- 1:max_multiplication

plot_width <- list()
plot_width[[1]] <- max_multiplication * planter_section_width


while (width < field_width) {
  t <- 2
  width <- plot_width[[1]]

  remainin_strip[[t]] <- plot_width[[t - 1]] + remainin_strip[[t - 1]] - harvester_width

  max_multiplication <- ceiling((harvester_width + remainin_strip) %/% planter_section_width)

  plot_width[[t]] <- max_multiplication * planter_section_width

  width <- width + plot_width[[t]]
}
```

# Create headland and experiment area

## Experiment field

```{r }
experiment_field <- st_buffer(field, - headland_buffer) %>%
  dplyr::select("geometry") %>%
  dplyr::mutate(type = "experiment")
```

```{r }
tm_shape(field) +
  tm_borders() +
tm_shape(experiment_field) +
  tm_borders(col = "red") 
```

## Headland

```{r }
headland <- st_difference(field, experiment_field) %>%
  dplyr::select("geometry") %>%
  dplyr::mutate(type = "headland")
```

```{r }
tm_shape(field) +
  tm_borders() +
tm_shape(headland) +
  tm_fill(col = "red", alpha = 0.5) 
```

## Whole field

```{r }
wholefield <- rbind(experiment_field, headland)
```

# Create Trial Design

## Set parameters

```{r }
wf_bbox <- st_bbox(wholefield)
cell_height <- conv_unit(10, "ft", "m")

starting_point <- c(wf_bbox["xmin"] - 100, wf_bbox["ymin"] - 100) 

#--- this should be defined above  ---#
plot_width <- conv_unit(30, "ft", "m")
```

## Make experiment grids

```{r }
all_grids <- make_trial_grids(
  field = experiment_field, 
  ab_line = ab_line, 
  starting_point = starting_point, 
  plot_width = plot_width, 
  cell_height = cell_height
)

tm_shape(wholefield) +
  tm_borders(lwd = 2) +
tm_shape(all_grids) +
  tm_polygons(col = "blue", alpha = 0.2) +
tm_shape(experiment_field) +
  tm_borders(col = "red", lwd = 2) 

```

```{r }
tm_shape(all_grids) +
  tm_fill(
    col = "group", 
    palette = "Spectral", 
    style = "order"
  ) + 
  tm_layout_to_add
```

```{r }
tm_shape(exp_grids_final) +
  tm_fill(
    col = "plot_id", 
    palette = "Spectral", 
    style = "order"
  ) + 
  tm_layout_to_add
```

## Assigning rates

```{r }

rate_ls <- seq(90, 240, by = 30)
trial_design <- assign_rates(all_grids, rate_ls)

```

```{r }

tm_shape(trial_design) +
  tm_fill(
    col = "rate", 
    palette = "YlGn", 
    style = "cat"
  ) + 
tm_shape(wholefield) +
  tm_borders() +
tm_layout_to_add


```



