# Read the analysis data 
# making changes to test

```{r data-prep, cache = F, results = "hide"}
data_sf <- here("Data/Growers", ffy, "Analysis-Ready/analysis_data.rds") %>% 
  readRDS() %>% 
  rename(yield = yield_vol) %>% 
  filter(!is.na(yield)) %>% 
  cbind(., st_coordinates(st_centroid(.)))

```

# GWR estimation for management zone delineation

## GWR estimation

```{r gwr, results = "hide"}
data_sf <- run_gwr(data_sf, "n_rate")

```

```{r }
ggplot(data_sf) +
  geom_histogram(
    aes(x = b_slope), 
    color = "blue", 
    fill = "white"
  )

```

## Define management zones based on GWR

```{r yield-response-functions-by-group}
data_sf <- define_mz(
  data_sf = data_sf, 
  max_num_zones = 4, 
  min_obs = 300
)

```

```{r }
tm_shape(data_sf) +
  tm_fill(col = "zone_txt", palette = "Set1") +
tm_layout_to_add

```

# Yield response function (GAM) estimation by zone

## GAM estimation by zone

```{r gam-estimate}
gam_res <- gam(
  yield ~ s(n_rate, k = 4, by = zone_txt) + s(X, k = 5) + s(Y, k = 5) + te(X, Y, k = c(5, 5)), 
  data = data_sf
) 

```

# Define grower-chose rate

```{r }

if (gc_type_n == "uniform") {

  data_sf <- mutate(data_sf, gc_rate = grower_chosen_rate_n) 

} else if (gc_type_n == "Rx") {

#/*----------------------------------*/
#' ## Read Rx data
#/*----------------------------------*/
  Rx_n <- st_read(Rx_file_n) %>% 
    st_set_crs(4326) %>% 
    st_transform(st_crs(data_sf)) %>%
    st_make_valid()

  dict_yield <- dictionary[type == "Rx-n", ]
  col_list <- dict_yield[, column]

  Rx_n <- make_var_name_consistent(
    Rx_n, 
    dict_yield 
  )

  #--- map ---#
  tm_shape(Rx_n) +
    tm_fill(col = "tgtn")

#/*----------------------------------*/
#' ## Identify grower-chosen rate by observation
#/*----------------------------------*/
  obs_tgts <- st_intersection(data_sf, Rx_n) %>% 
    mutate(area = as.numeric(st_area(.))) %>% 
    data.table() %>% 
    .[, .SD[area == max(area)], by = obs_id] %>% 
    .[, num_obs_per_zone := .N, tgtn] %>% 
    .[, analyze := FALSE] %>% 
    .[num_obs_per_zone >= 200, analyze := TRUE] %>% 
    .[, .(obs_id, tgtn, analyze)] 

  data_sf <- left_join(data_sf, obs_tgtn, by = "obs_id") %>% 
    rename(gc_rate = tgtn)

}

```

# Profit estimation and economic optimization

## Yield-Profit Estimation (at hypothetical points)

```{r }
#/*----------------------------------*/
#' ## Evaluation data (hypothetical points)
#/*----------------------------------*/
eval_data <- predict_yield_pi(
    data = data_sf, 
    est = gam_res, 
    var_name = "n_rate", 
    by = "zone_txt"
  ) %>% 
  .[, type := "opt_v"]%>% 
  .[, .(
    n_rate, zone_txt, type, yield_hat, yield_hat_se,
    profit_hat, profit_hat_se
  )] 

#--- assign grower-chosen rate ---#

if (gc_type_n == "uniform") {
  gc_rate_data <- data.table(data_sf) %>% 
    unique(by = "zone") %>% 
    .[, n_rate := grower_chosen_rate_n]  

  eval_data_gc <- predict_yield_pi_simple(
      data = gc_rate_data, 
      est = gam_res,
      var_name = "n_rate"
    ) %>% 
    .[, type := "gc"] %>% 
    .[, .(
      n_rate, zone_txt, type, yield_hat, yield_hat_se,
      profit_hat, profit_hat_se
    )]

  eval_data <- rbind(eval_data, eval_data_gc)

}

#/*----------------------------------*/
#' ## Yield response functions by zone
#/*----------------------------------*/

ymin <- eval_data[, min(yield_hat - 1.96 * yield_hat_se)] - 10

eval_data %>% 
  filter(type == "opt_v") %>% 
  ggplot(data = .) +
  geom_line(aes(y = yield_hat, x = n_rate)) +
  geom_ribbon(
    aes(
      ymin = yield_hat - 1.96 * yield_hat_se, 
      ymax = yield_hat + 1.96 * yield_hat_se, 
      x = n_rate
    ),
    fill = "red",
    alpha = 0.4
  ) +
  facet_grid(. ~ zone_txt) +
  ylim(ymin, NA)

```

## Optimal Variable Nitrogen Rate

```{r gen-opt-N-v-data-map}
opt_n_data <- eval_data %>% 
  .[type == "opt_v", ] %>% 
  .[, .SD[profit_hat == max(profit_hat), ], by = zone_txt] %>% 
  setnames("n_rate", "opt_n") 

#--- assign opt_n to each observation ---#
data_sf <- left_join(
  data_sf, 
  opt_n_data[, .(zone_txt, opt_n)], 
  by = "zone_txt"
)

if (gc_type_n == "uniform") {

  opt_gc_data <- copy(opt_n_data) %>% 
    setnames("opt_n", "n_rate") %>% 
    rbind(., eval_data[type == "gc",]) %>% 
    .[, pi_upper := profit_hat + profit_hat_se * 1.96] %>% 
    .[, pi_lower := profit_hat - profit_hat_se * 1.96]

}

  
```

## Optimal Uniform Nitrogen Rate

```{r get-opt-S-u}
data_sf <- mutate(
  data_sf, 
  opt_n_u = find_opt_u(data_sf, "n_rate", gam_res)
)

```

# Profit differential at each observation

```{r }
pi_data_opt <- data_sf %>% 
  data.table() %>% 
  .[, .(opt_n, X, Y, zone_txt, obs_id)] %>% 
  setnames("opt_n", "n_rate") %>% 
  predict_yield_pi_simple(., gam_res, "n_rate") %>% 
  .[, .(obs_id, zone_txt, profit_hat)] %>% 
  .[, type := "opt_v"]
  
pi_data_gc <- data_sf %>% 
  data.table() %>% 
  .[, .(gc_rate, X, Y, zone_txt, obs_id)] %>% 
  setnames("gc_rate", "n_rate") %>% 
  predict_yield_pi_simple(., gam_res, "n_rate") %>% 
  .[, .(obs_id, zone_txt, profit_hat)] %>% 
  .[, type := "gc"]
  
pi_data_indiv_sf <- rbind(pi_data_opt, pi_data_gc) %>% 
  .[order(obs_id, type), ] %>% 
  .[, pi_dif := diff(profit_hat), by = obs_id] %>% 
  left_join(., dplyr::select(data_sf, obs_id), by = "obs_id") %>% 
  st_as_sf()

# ggplot(pi_data_indiv) +
#   geom_sf(aes(fill = pi_dif))

```

# Statistical testing

## Profit by zone

```{r }

if (gc_type_n == "uniform") {

  data_for_test <- data.table(data_sf) %>% unique(by = "zone_txt")

  pi_dif_test_zone <- get_dif_stat_zone(
    data = data_for_test, 
    test_var = "n_rate", 
    opt_var = "opt_n",
    gc_var = "gc_rate",
    gam_res = gam_res,
    by_var = "zone_txt"
  )

} else {

  pi_dif_test_zone <- get_dif_stat_zone(
    data = data.table(data_sf), 
    test_var = "n_rate", 
    opt_var = "opt_n",
    gc_var = "gc_rate",
    gam_res = gam_res,
    by_var = "zone_txt"
  )

  mean_gc_rate_by_zone <- data.table(data_sf)[, .(n_rate = mean(gc_rate)), by = zone_txt]

  gc_data <- pi_dif_test_zone %>% 
    .[, .(yhat_est_gc, point_est_gc, point_est_gc_se, zone_txt)] %>% 
    mean_gc_rate_by_zone[., on = "zone_txt"] %>% 
    setnames(
      c("yhat_est_gc", "point_est_gc", "point_est_gc_se"), 
      c("yield_hat", "profit_hat", "profit_hat_se")
    ) %>% 
    .[, `:=`(
      pi_upper = profit_hat + 1.96 * profit_hat_se,
      pi_lower = profit_hat - 1.96 * profit_hat_se
    )] %>% 
    .[, type := "gc"]

  opt_data <- pi_dif_test_zone %>% 
    .[, .(yhat_est_opt, point_est_opt, point_est_opt_se, zone_txt)] %>% 
    opt_n_data[, .(zone_txt, opt_n)][., on = "zone_txt"] %>% 
    setnames(
      c("yhat_est_opt", "point_est_opt", "point_est_opt_se", "opt_n"), 
      c("yield_hat", "profit_hat", "profit_hat_se", "n_rate")
    ) %>% 
    .[, `:=`(
      pi_upper = profit_hat + 1.96 * profit_hat_se,
      pi_lower = profit_hat - 1.96 * profit_hat_se
    )] %>% 
    .[, type := "opt_v"]

  opt_gc_data <- rbind(opt_data, gc_data)

}
 
 
```

## Whole-field profit

```{r }
test_data <- data.table(data_sf) 

whole_profits_test <- rbind(
  #--- opt (V) vs gc ---#
  get_dif_stat(
    test_data, 
    "n_rate", 
    "opt_n", 
    "gc_rate",
    gam_res
  ) %>% 
  .[, type := "optimal site-specific rate strategy \n vs \n grower-chosen strategy"] %>% 
  .[, type_short := "ovg"],

  #--- opt (u) vs gc ---#
  get_dif_stat(
    test_data, 
    "n_rate", 
    "opt_n", 
    "opt_n_u",
    gam_res
  ) %>% 
  .[, type := "optimal site-specific rate strategy \n vs \n optimal uniform rate strategy"] %>% 
  .[, type_short := "ovou"],

  #--- opt (u) vs gc ---#
  get_dif_stat(
    test_data, 
    "n_rate", 
    "opt_n_u", 
    "gc_rate",
    gam_res
  ) %>% 
  .[, type := "optimal uniform rate strategy \n vs \n grower-chosen strategy"] %>% 
  .[, type_short := "oug"]
)
  
```

# Create figures of yield response functions by character

```{r }
ys_by_char <- make_ys_by_chars(data_sf)
```


# Save the results

```{r }
results <- tibble(
  data_sf = list(data_sf),
  ys_by_char = list(ys_by_char),
  eval_data = list(eval_data),
  opt_gc_data = list(opt_gc_data),
  pi_data_indiv_sf = list(pi_data_indiv_sf),
  pi_dif_test_zone = list(pi_dif_test_zone),
  whole_profits_test = list(whole_profits_test)
)  

saveRDS(results, here("Reports", "Growers", ffy, "analysis_results_n.rds"))
```


